### 2017-08-06 paper/incomeShocks-jde-r1.tex
Add file with birth/pregnancy results

\begin{table}[htbp]
\begin{center}
\begin{threeparttable}
\caption{The Effects of Crop Loss on Pregnancy and Births}
\label{tab:birth}
\begin{tabular}{@{} l D{.}{.}{1.5} D{.}{.}{1.5} D{.}{.}{1.5} D{.}{.}{1.5} D{.}{.}{1.5} D{.}{.}{1.5}  @{}}
\toprule
                                                       &\multicolumn{3}{c}{Currently pregnant}&\multicolumn{3}{c}{Birth since last survey}\\ \cmidrule(lr){2-4} \cmidrule(lr){5-7}
                                                       &                     & \mct{Fixed Effects}                       &                     & \mct{Fixed Effects}                       \\ \cmidrule(lr){3-4} \cmidrule(lr){6-7}
                                                       & \mco{OLS}           & \mco{Community}     & \mco{Woman}         & \mco{OLS}           & \mco{Community}     & \mco{Woman}         \\ \midrule
Crop loss - 1-7 months                                 &      -0.053         &      -0.074\sym{*}  &      -0.093\sym{**} &                     &                     &                     \\
\hs (200 TZS or above)                                 &     (0.038)         &     (0.039)         &     (0.043)         &                     &                     &                     \\
Crop loss - 7-14 months                                &                     &                     &                     &      -0.103\sym{***}&      -0.115\sym{***}&      -0.159\sym{***}\\
\hs (200 TZS or above)                                 &                     &                     &                     &     (0.040)         &     (0.042)         &     (0.050)         \\
Wave dummies                                           &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Community fixed effects                                &    \mco{No}         &    \mco{Yes}        &    \mco{No}         &    \mco{No}         &    \mco{Yes}        &    \mco{No}         \\
Woman fixed effects                                    &    \mco{No}         &    \mco{No}         &    \mco{Yes}        &    \mco{No}         &    \mco{No}         &    \mco{Yes}        \\
Observations                                           &    \mco{988}        &    \mco{988}        &    \mco{988}        &    \mco{741}        &    \mco{741}        &    \mco{741}        \\
Number of women                                        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        \\
\bottomrule    
\end{tabular}
\begin{tablenotes} \footnotesize
\item \hspace*{-0.5em} \textbf{Note.}
All models are linear probability models.
Robust standard errors clustered at household level in parentheses; 
* significant at 10\%; ** significant at 5\%; *** significant at 1\%.
Crop loss is a dummy for a per capita crop loss of 200 TZS or above.
% Assets are per capita and measured in 10,000 TZS.
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

>>>>

% Table with pregnancy and birth results
\input{../tables/main_pregnant_birth.tex}
